Programmer friendly communication framework

### 2024-03-09 2024_paper/paper/msglink_framework.tex
added code example, finished paper for now

>>>>

The following is a compressed code example of how one might define a msglink link in C++. The explanation of the code example is beyond the scope of this paper.

\begin{code-cpp}
// structure name is event name
struct my_event 
    : public msglink::incoming_event {
    int a;
    std::string b;
    EL_MSGLINK_DEFINE_INCOMING_EVENT(
        my_event, a, b
    )
};
class my_link : public msglink::link {
    using link::link;
    EL_MSGLINK_LINK_VERSION(1);
    msglink::event_sub_hdl_ptr my_sub;
    void handle_my_event(in_event &_evt) {
        std::cout << _evt.a << _evt.b;
    }
public:
    virtual void define() noexcept override {
        my_sub = define_event<my_event>(
            &my_link::handle_my_event
        );
    }
};
\end{code-cpp}
